---
title: "Bing machine analysis"
author: "Zeynep Civelek"
date: "July 6, 2020"
output: word_document
---

```{r}
#PREPARE
R.Version()#for referencing, shows you which R version you are using
rm(list=ls())#removes any other items in your workspace
ls()#check whether workspace is empty
```

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = "C:\\")
```

```{r}
#LOAD DATA AND LIBRARIES
setwd("C:/Users/Zeynep/Desktop/EF-analyses")#sets the working directory, this is where your datafile is
bing <-read.csv("bing_data.csv",header=TRUE)
library(lme4)
library(readr)
library(tidyverse)
library(sjPlot)
library(ggthemes)
library(gridExtra)
library(reshape2)
library(car)
library("ggpubr")
library(dplyr)
```

```{r}
#OVERVIEW
str(bing)

#recode variables
bing$id <- as.factor(bing$id)
bing$Age_group <- as.factor(bing$Age_group)

levels(bing$Age_group)

str(bing)
```


# Dropouts
```{r}
dropouts<-subset(bing, Dropout == "yes")
```
We have 5 dropouts (1 child stopped after 4 trials, 1 child stopped after 8 trials, 1 child stopped after 9 trials, 1 child where RA gave away the game by saying "let's watch and listen", 1 child with an experimenter error in trial 11 (wrong noise) so we only had 10 trials).

# Which children to include?
We eventually decided to include children who have completed 75% (i.e., 15 trials) of the test trials. So I'm removing these 5 children from further analyses.

# Removing the dropouts from data
```{r}
bingvalid<-subset(bing, Dropout=="no")
#aggregating by ID to see the sample size
bing_individual <- bingvalid %>%
  group_by(id, Gender, Age_months, Midtesting_age_months, Midtesting_age_group, Median_split_age) %>%
  summarize(Success_in0and1 = mean(Success_in0and1))%>%
  ungroup()%>%
  group_by(Midtesting_age_group)%>%
  add_count(Success_in0and1)
```

Final **sample size is 65**.

# Sample description
## Gender distribution
```{r}
table(bing_individual$Gender)
table(bing_individual$Gender, bing_individual$Midtesting_age_group)
boys <- subset(bing_individual, Gender == "m")
girls <- subset(bing_individual, Gender == "f")
hist(boys$Midtesting_age_group)
shapiro.test(boys$Midtesting_age_group)#is not normally distributed
hist(girls$Midtesting_age_group)
shapiro.test(girls$Midtesting_age_group)#is not normally distributed
wilcox.test(bing_individual$Midtesting_age_group ~ bing_individual$Gender, alternative = "two.sided")
```
There are **39 girls** and **26 boys**.

- Girls: 22 3y, 14 4y, 3 5y
- Boys: 10 3y, 12 4y, 4 5y

There is no difference in the age distribution between boys and girls.

## Age
### Age at beginning of testing
```{r}
mean(bing_individual$Age_months)
sd(bing_individual$Age_months)
min(bing_individual$Age_months)
max(bing_individual$Age_months)
table(bing_individual$Age_months)
```
At the beginning of testing, the children who had valid data on the Bing Machine task were on average 47.57 months (SD = 6.93, range 36-64) old. There were 34 3-year-olds, 26 4-year-olds, and 5 5-year-olds.

### Age in the middle of testing
```{r}
mean(bing_individual$Midtesting_age_months)
sd(bing_individual$Midtesting_age_months)
min(bing_individual$Midtesting_age_months)
max(bing_individual$Midtesting_age_months)
table(bing_individual$Midtesting_age_months)
```
In the middle of testing, the children who had valid data on the Bing Machine task were on average **49.29 months (SD = 6.90, range 39-65)** old. There were 

- 32 3-year-olds
- 26 4-year-olds
- 7 5-year-olds

### Age mediansplit by entire sample
Median is 49 months

```{r}
table(bing_individual$Median_split_age)
```

There are **34 young** and **31 old** children.

# Warm-up
```{r}
levels(bingvalid$Training_Crit_reached)
```
All children (N=65) passed the transparent training within 3 trials (the minimum number of required trials to pass).


